Tabular Constraint Learning

### 2016-05-04 Paper/ECAI/tabular.tex
Added more evaluation data
first stab at abstract

\begin{abstract}
  abstract
\end{abstract}

@@

@@

\subsubsection*{Q3. How fast is the algorithm?}
Concerning the speed of the algorithm we also prioritized accuracy when a trade-off had to be made.
For the 32 spreadsheets in the benchmark our implementation ran in $17.86s \pm 0.87s$.
The execution times vary widely though between spreadsheets, only four spreadsheets taking more than $0.2s$.
Most of the execution time in these cases goes towards searching either aggregate constraints or conditional aggregates.
The search for aggregates will be slow on spreadsheets containing larger groups of numeric data.
For conditional aggregates the number of candidate primary keys (all-different) and numeric vectors determines the running time (e.g. the case study example).

\paragraph{Dependencies}
In order for the algorithm to run efficiently it is crucial to use dependencies and find constraint incrementally whenever possible.
This avoids some of the explosion of combinations for constraints that have many arguments.
For example, using foreign keys as a base constraint to find conditional aggregates reduces the running time for the case study from about 3 seconds to below 1 second.
Unfortunately, this assumption is sometimes too strong, when users are interested in aggregates for only some of the keys that are present in the data.

\sergey{Add summary table of results}

>>>>

\begin{abstract}
Spreadsheets, comma separated value files and other tabular data representations are in wide use today. However, the correct use and maintenance of functions in and between the tabular data can be error-prone and overwhelming. In this work, we investigate the automatic discovery of constraints (functions and relations) from raw tabular data. Our method takes inspiration form inductive logic programming and constraint satisfiability. We represent common spreadsheet functions as predicates with arguments that must satisfy number of constraints over the arguments. This allows generic constraint satisfaction techniques to be used to find all such satisfying predicates/functions within the rows, columns and submatrices of the tables. We show the effectiveness and accuracy of this approach on a number of spreadsheets from varying sources.
\end{abstract}

@@

\newcommand{\runtotal}{16.12}
\newcommand{\runtotalstd}{0.62}

\newcommand{\runfile}{0.50}
\newcommand{\runfilestd}{0.02}

@@

\subsubsection*{Q3. How fast is the algorithm?}
Concerning the speed of the algorithm we also prioritized accuracy when a trade-off had to be made.
For the 32 spreadsheets in the benchmark our implementation ran in ${\runtotal}s \pm {\runtotalstd}s$.
The execution times vary widely though between spreadsheets, only four spreadsheets taking more than $0.2s$.
Most of the execution time in these cases goes towards searching either aggregate constraints or conditional aggregates.
The search for aggregates will be slow on spreadsheets containing larger groups of numeric data.
For conditional aggregates the number of candidate primary keys (all-different) and numeric vectors determines the running time (e.g. the case study example).

\begin{table}
  \centering
  \begin{tabular}{lll}
    & \textbf{Total} & \textbf{Average per spreadsheet} \\
    \textbf{Essential constraints} & $93$ & $2.91$ \\
    \textbf{Accuracy} & $96.77\%$ & $94.27\%$ \\
    \textbf{Redundant} & $23.14\%~(28)$ & $8.33\%~(0.88)$ \\
    \textbf{Speed (s)} & ${\runtotal}s \pm {\runtotalstd}s$ & ${\runfile}s \pm {\runfilestd}s$
  \end{tabular}
  \caption{Overview evaluation on essential constraints}
\end{table}

\paragraph{Dependencies}
In order for the algorithm to run efficiently it is crucial to use dependencies and find constraint incrementally whenever possible.
This avoids some of the explosion of combinations for constraints that have many arguments.
For example, using foreign keys as a base constraint to find conditional aggregates reduces the running time for the case study from about 3 seconds to below 1 second.
Unfortunately, this assumption is sometimes too strong, when users are interested in aggregates for only some of the keys that are present in the data.
\sergey{Add summary table of results}
